---
title: "ch003"
author: "Daniel_Kim"
date: '2019 12 15 '
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gdata)
library(broom)
# install.packages('sigr')
library(sigr)
library(vtreat)
```


### Catogorical Variables...

 Call str on flowers to see the types of each column

```{r, message = FALSE}
# install.packages('Sleuth3')
library(Sleuth3)
```

```{r, message = FALSE}
flowers <- case0901
flowers %>%
  mutate(Time = ifelse(Time == 1, "Late", "Early")) -> flowers
flowers %>% head
```


Use unique() to see how many possible values Time takes

```{r}
unique(flowers$Time)
```


 Build a formula to express Flowers as a function of Intensity and Time: fmla. Print it
 
```{r}
(fmla <- as.formula("Flowers ~ Intensity + Time"))
```
 
Use fmla and model.matrix to see how the data is represented for modeling

```{r}
mmat <- model.matrix(fmla, flowers)
mmat
```


 Examine the first 20 lines of flowers
 
```{r}
head(flowers, 20)
```
 

 Examine the first 20 lines of mmat

```{r}
head(mmat, 20)
```


Fit a model to predict Flowers from Intensity and Time : flower_model

```{r}
flower_model <- lm(fmla, data= flowers)
```

Use summary on mmat to remind yourself of its structure

```{r}
summary(mmat)
```

Use summary to examine flower_model 

```{r}
summary(flower_model)
```


Predict the number of flowers on each plant

```{r}
flowers$predictions <- predict(flower_model, flowers)
```


Plot predictions vs actual flowers (predictions on x-axis)

```{r}
ggplot(flowers, aes(x = predictions, y = Flowers)) + 
  geom_point() +
  geom_abline(color = "blue") 
```

### Interactions

Data alcohol loading...

```{r}
# str(case1101)
alcohol <- case1101
str(alcohol)
```

```{r}
summary(alcohol)
```


Create the formula with main effects only
Gastric : 위, Metabol : 물질대사

```{r}
(fmla_add <- Metabol ~ Gastric + Sex)
```

Create the formula with interactions
Gastric은 주요 영향 요인이지만 Sex는 아니므로 교호작용 항만 추가합니다.

```{r}
(fmla_interaction <- Metabol ~ Gastric + Gastric:Sex)
```

Fit the main effects only model

```{r}
model_add <- lm(fmla_add, data = alcohol)
```

Fit the interaction model

```{r}
model_interaction <- lm(fmla_interaction, data =  alcohol)
```

Call summary on both models and compare

```{r}
summary(model_add)
```


```{r}
summary(model_interaction)
```

Create the splitting plan for 3-fold cross validation

```{r}
set.seed(34245)  # set the seed for reproducibility
splitPlan <- kWayCrossValidation(nrow(alcohol), 3, NULL, NULL)
```


Sample code: Get cross-val predictions for main-effects only model

```{r}
alcohol$pred_add <- 0  # initialize the prediction vector
for(i in 1:3) {
  split <- splitPlan[[i]]
  model_add <- lm(fmla_add, data = alcohol[split$train, ])
  alcohol$pred_add[split$app] <- predict(model_add, newdata = alcohol[split$app, ])
}
```


Get the cross-val predictions for the model with interactions

```{r}
alcohol$pred_interaction <- 0 # initialize the prediction vector
for(i in 1:3) {
  split <- splitPlan[[i]]
  model_interaction <- lm(fmla_interaction, data = alcohol[split$train, ])
  alcohol$pred_interaction[split$app] <- predict(model_interaction, newdata = alcohol[split$app, ])
}
```


Get RMSE

```{r}
alcohol %>% 
  gather(key = modeltype, value = pred, pred_add, pred_interaction) %>%
  mutate(residuals = Metabol - pred) %>%      
  group_by(modeltype) %>%
  summarize(rmse = sqrt(mean(residuals^2))) # residuals^2 에 유의할 것...
```

### Transforming the response before modeling...

```{r}
load('./data/Income.RData')
```


Examine Income2005 in the training set

```{r}
income_train <- incometrain
income_test <- incometest
```

```{r}
str(income_train)
```

$Income2005 : Percentile on the Armed Forces Qualifying Test...


```{r}
summary(income_train$Income2005)
```

```{r}
ggplot(income_train, aes(Income2005)) + geom_histogram()
```


Write the formula for log income as a function of the tests and print it

```{r}
(fmla.log <- log(Income2005) ~ Arith + Word + Parag + Math + AFQT)
```

Fit the linear model

```{r}
model.log <-  lm(fmla.log, data = income_train)
```

Make predictions on income_test

```{r}
income_test$logpred <- predict(model.log, income_test)
```


```{r}
summary(income_test$logpred)
```

Convert the predictions to monetary units

```{r}
income_test$pred.income <- exp(income_test$logpred)
```

```{r}
summary(income_test$pred.income)
```

```{r}
head(income_test)
```


Plot predicted income (x axis) vs income

```{r}
ggplot(income_test, aes(x = pred.income, y = Income2005)) + 
  geom_point() + 
  geom_abline(color = "blue")
```

setting fmla.abs 

```{r}
fmla.abs <- Income2005 ~ Arith + Word + Parag + Math + AFQT
```

```{r}
fmla.abs
```

model.abs 

```{r}
model.abs <- lm(fmla.abs, data = income_train)
```


```{r}
summary(model.abs)
```

Add predictions to the test set

```{r}
income_test <- income_test %>%
  mutate(pred.absmodel = predict(model.abs, income_test),        # predictions from model.abs
         pred.logmodel = exp(predict(model.log, income_test)))   # predictions from model.log

```


Gather the predictions and calculate residuals and relative error

```{r}
income_test %>% 
  gather(key = modeltype, value = pred, pred.absmodel, pred.logmodel) %>% head
```


```{r}
income_long <- income_test %>% 
  gather(key = modeltype, value = pred, pred.absmodel, pred.logmodel) %>%
  mutate(residual = pred - Income2005,   # residuals
         relerr   = residual / Income2005)   # relative error
```

```{r}
head(income_long)
```


Calculate RMSE and relative RMSE and compare

```{r}
income_long %>% 
  group_by(modeltype) %>%      # group by modeltype
  summarize(rmse     = sqrt(mean(residual^2)),    # RMSE
            rmse.rel = sqrt(mean(relerr^2)))    # Root mean squared relative error
```

`houseprice` data loading...

```{r}
houseprice <- readRDS('./data/houseprice.rds')
summary(houseprice)
```

Create the formula for price as a function of squared size

```{r}
(fmla_sqr <- price ~ I(size^2))
```

Fit a model of price as a function of squared size (use fmla_sqr)

```{r}
model_sqr <- lm(fmla_sqr, data = houseprice)
```

Fit a model of price as a linear function of size

```{r}
model_lin <- lm(price ~ size, data = houseprice)
```

Make predictions and compare

```{r}
houseprice %>% 
    mutate(pred_lin = predict(model_lin, houseprice),       # predictions from linear model
           pred_sqr = predict(model_sqr, houseprice)) %>%   # predictions from quadratic model 
    gather(key = modeltype, value = pred, pred_lin, pred_sqr) %>% # gather the predictions
    ggplot(aes(x = size)) + 
       geom_point(aes(y = price)) +                   # actual prices
       geom_line(aes(y = pred, color = modeltype)) + # the predictions
       scale_color_brewer(palette = "Dark2")
```


Create a splitting plan for 3-fold cross validation

```{r}
set.seed(34245)  # set the seed for reproducibility
splitPlan <- kWayCrossValidation(nrow(houseprice), 3, NULL, NULL)
```

Sample code: get cross-val predictions for price ~ size

```{r}
houseprice$pred_lin <- 0  # initialize the prediction vector
for(i in 1:3) {
  split <- splitPlan[[i]]
  model_lin <- lm(price ~ size, data = houseprice[split$train,])
  houseprice$pred_lin[split$app] <- predict(model_lin, newdata = houseprice[split$app,])
}
```

Get cross-val predictions for price as a function of size^2 (use fmla_sqr)

```{r}
houseprice$pred_sqr <- 0 # initialize the prediction vector
for(i in 1:3) {
  split <- splitPlan[[i]]
  model_sqr <- lm(price ~ I(size^2), data = houseprice[split$train, ])
  houseprice$pred_sqr[split$app] <- predict(model_sqr, newdata = houseprice[split$app, ])
}
```

Gather the predictions and calculate the residuals

```{r}
houseprice_long <- houseprice %>%
  gather(key = modeltype, value = pred, pred_lin, pred_sqr) %>%
  mutate(residuals = pred - price)
```

Compare the cross-validated RMSE for the two models

```{r}
houseprice_long %>% 
  group_by(modeltype) %>% # group by modeltype
  summarize(rmse = sqrt(mean(residuals^2)))
```

