---
title: "ch001"
author: "Daniel_Kim"
date: '2019 12 15 '
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gdata)
library(broom)
# install.packages('sigr')
library(sigr)
```


```{r, message=FALSE}
unemployee <- read_csv('./data/s_data.csv')
unemployee
```

```{r}
summary(unemployee)
```

Set formula...

```{r}
fmla <- Y ~ X
```

```{r}
fmla
```

```{r}
unemployee_model <- lm(fmla, data = unemployee)
```


Call summary() on unemployment_model to get more details

```{r}
summary(unemployee_model)
```


Call glance() on unemployment_model to see the details in a tidier form

```{r}
glance(unemployee_model)
```


Call wrapFTest() on unemployment_model to see the most relevant details

```{r}
wrapFTest(unemployee_model)
```


unemployment is in your workspace

```{r}
unemployment <- unemployee %>%
  rename(male_unemployment = X, female_unemployment = Y)
summary(unemployment)
```

```{r}
unemployee_model <- lm(female_unemployment ~ male_unemployment, data = unemployment)
```


newrates is in your workspace
```{r}
newrates <- data.frame(male_unemployment = 5)
newrates
```


Predict female unemployment in the unemployment data set

```{r}
unemployment$predictions <- predict(unemployee_model, unemployment)
```

Make a plot to compare predictions to actual (prediction on x axis). 

```{r}
ggplot(unemployment, aes(x = predictions, y = female_unemployment)) + 
  geom_point() +
  geom_abline(color = "blue")
```


Predict female unemployment rate when male unemployment is 5%

```{r}
pred <- predict(unemployee_model, newrates)
```

Print it

```{r}
pred
```

### Multivariate linear regression (Part 1)

```{r}
bloodpressure <- readRDS('./data/bloodpressure.rds')
```

```{r}
summary(bloodpressure)
```

```{r}
fmla <- blood_pressure ~ age + weight
```

```{r}
bloodpressure_model <- lm(fmla, data = bloodpressure)
```

```{r}
bloodpressure
```

```{r}
summary(bloodpressure_model)
```

Predict blood pressure using bloodpressure_model

```{r}
bloodpressure$prediction <- predict(bloodpressure_model, data = bloodpressure)
```

Plot the result...

```{r}
ggplot(bloodpressure, aes(prediction, blood_pressure)) +
  geom_point() +
  geom_abline(color = 'blue')
```

### Collinearity
Collinearity -- when variables are partially correlated.
Coefficients might change sign

```{r}
save(unemployee_model, unemployment, file = 'unemp.RData')
```

